Untitled

### 2024-01-04 manuscript_revised.RMD
further revision

**Purpose:** Resistance training-induced skeletal muscle hypertrophy seems to depend on ribosome biogenesis and content. High glucose treatment may augment ribosomal biogenesis, as evident from *in vitro* studies, and may thus act to potentiate resistance training-induced adaptations *in vivo*. This was investigated with the main outcomes being total RNA and ribosomal RNA abundances, as well as relevant transcriptional or translational regulators (c-Myc/UBF/rpS6) to further describe the relationship between these regulators and ribosome biogenesis in human skeletal muscle tissue.

@@

The dietary intervention spanned the whole day, divided into three periods: I) From awakening until 2.5 hours (hrs) after RT, II) from 2.5 hours after RT until 2200hrs, and III) from 2200hrs until awakening. During period I, participants ingested protein and glucose *or* protein and placebo only. Glucose/placebo was ingested three times in period I: 30 minutes before RT (0830hrs, 30g vs. 0g glucose), immediately before RT (0900hrs, 30g vs. 0g glucose), and immediately after RT (\~0930hrs, 30g vs. 0g glucose). Whey Protein Isolate (Proteinfabrikken, Stokke, Norway) was ingested 2hrs before RT (0700hrs) and immediately after RT (\~0930hrs), in boluses of 25 g mixed with 150 ml water. In the afternoon (1800hrs-1900hrs, period II) participants ingested glucose or placebo (3x30g vs. 3x0g glucose) opposite to the supplement they received during RT, to ensure a balanced daily intake of glucose. Apart from this, participants ingested a self-chosen diet during period II, registered in MyFitnessPal or similar applications. The self-chosen diet was repeated on pairwise consecutive days, to ensure similar premises for resistance training responses between conditions. During period III (2200-0700hrs), participants remained in an overnight fasted state. The daily onset of the dietary intervention (i.e., first ingestion of protein supplement) varied between participants, from 0600hrs to 0900hrs to allow multiple participants to complete the protocol simultaneously. During sessions, participants were free to ingest water ad libitum.

>>>>

**Purpose:** Resistance training-induced skeletal muscle hypertrophy seems to depend on ribosome biogenesis and content. High glucose treatment may augment ribosomal biogenesis, as evident from *in vitro* studies, and may thus act to potentiate resistance training-induced adaptations *in vivo*. This was investigated with total RNA and ribosomal RNA abundances as main outcomes, with relevant transcriptional or translational regulators (c-Myc/UBF/rpS6) as a secondary outcome.

@@

The dietary intervention spanned the whole day, divided into three periods: I) From awakening until 2.5 hours (hrs) after RT, II) from 2.5 hours after RT until 2200hrs, and III) from 2200hrs until awakening. During period I, participants ingested protein and glucose *or* protein and placebo only. Glucose/placebo was ingested three times in period I: 30 minutes before RT (0830hrs, 30g vs. 0g glucose), immediately before RT (0900hrs, 30g vs. 0g glucose), and immediately after RT (\~0930hrs, 30g vs. 0g glucose). Whey Protein Isolate (Proteinfabrikken, Stokke, Norway) was ingested 2hrs before RT (0700hrs) and immediately after RT (\~0930hrs), in boluses of 25 g mixed with 150 ml water. In the afternoon (1800hrs-1900hrs, period II) participants ingested glucose or placebo (3x30g vs. 3x0g glucose) opposite to the supplement they received during RT, to ensure a balanced daily intake of glucose. Apart from this, participants ingested a self-chosen diet during period II. Further, participants were asked not to use any other supplements such as additional protein and/or creatine, and to register all food/drink consumption in MyFitnessPal or similar applications. The self-chosen diet was repeated on pairwise consecutive days, to ensure similar premises for resistance training responses between conditions. During period III (2200-0700hrs), participants remained in an overnight fasted state. The daily onset of the dietary intervention (i.e., first ingestion of protein supplement) varied between participants, from 0600hrs to 0900hrs to allow multiple participants to complete the protocol simultaneously. During sessions, participants were free to ingest water ad libitum.

### 2024-01-04 resources/older manuscript versions/revision_notes.RMD
further revision

Reviewer 1, comment 1: 25,000 dilution for primary seems quite diluted. Is the dilution is correct? Page 9, line 257-258 (line 211 in quarto)
 - Original draft: Antibodies were diluted in blocking buffer to concentrations corresponding to 1:25 000 (UBF, rpS6) and 1:5000 (c-Myc).
 - Authors comment: By mistake, only the dilution volumes of the secondary antibodies were included in the original description. This section is now updated with dilution volumes of both primary and secondary antibodies. 
 - Revision: Antibodies were diluted in blocking buffer to concentrations corresponding to 1:500 (UBF and rpS6, primary), 1:2000 (c-Myc, primary), 1:5000 (c-Myc, secondary) and 1:25 000 (UBF, rpS6, secondary).

@@

Reviewer 2, comment 1: Please, also describe in the abstract the second objective of the study (lines 98-99). The abstract does not state, and, therefore is not clear, what are the main outcomes (parameters) measured in the clinical trial.
 - Authors comment: The abstract has now been updated with this information.
 - Revision:
   - Removed "However, this remains largely unexplored."
   - Added "This was investigated with the main outcomes being total RNA and ribosomal RNA abundances, as well as relevant transcriptional or translational regulators (c-Myc/UBF/rpS6) to further described relationship between these regulators and ribosome biogenesis in human skeletal muscle tissue."
   - Abstract trenger nå mer jobb, for å kutte ned til akseptert lengde/antall ord.

@@

Reviewer 2, comment 3: There is a lack of information regarding the use of supplements by participants. This aspect is important for characterizing the sample and as stated by the authors on page 3, line 57.

>>>>

Reviewer 1, comment 1: 25,000 dilution for primary seems quite diluted. Is the dilution is correct? Page 9, line 257-258 (line 211 in quarto) 
- Original draft: Antibodies were diluted in blocking buffer to concentrations corresponding to 1:25 000 (UBF, rpS6) and 1:5000 (c-Myc). 
- Authors answer: By mistake, only the dilution volumes of the secondary antibodies were included in the original description. This section is now updated with dilution volumes of both primary and secondary antibodies. 
- Revision: Antibodies were diluted in blocking buffer to concentrations corresponding to 1:500 (UBF and rpS6, primary), 1:2000 (c-Myc, primary), 1:5000 (c-Myc, secondary) and 1:25 000 (UBF, rpS6, secondary).

@@

Reviewer 2, comment 1: Please, also describe in the abstract the second objective of the study (lines 98-99). The abstract does not state, and, therefore is not clear, what are the main outcomes (parameters) measured in the clinical trial. 
- Authors comment: The abstract has now been updated with this information. 
- Revision: 
  - Removed "However, this remains largely unexplored." 
  - Added "This was investigated with total RNA and ribosomal RNA abundances as main outcomes, with relevant transcriptional or translational regulators (c-Myc/UBF/rpS6) as a secondary outcome." 
- Abstract trenger nå mer jobb, for å kutte ned til akseptert lengde/antall ord. Er det ok med 30 ord for mye?

@@

Reviewer 2, comment 3: There is a lack of information regarding the use of supplements by participants. This aspect is important for characterizing the sample and as stated by the authors on page 3, line 57.
 - Authors comment: The participants were asked not to use any other form of supplements during the course of the study. However, I can see that this is not clearly stated in the methods chapter, and will now be added. 
 - Revision: Page 5, lines 141-143.
   - "Apart from this, participants ingested a self-chosen diet during period II, registered in MyFitnessPal or similar applications" changed to "Apart from this, participants ingested a self-chosen diet during period II. Further, participants were asked not to use any other supplements such as additional protein and/or creatine, and to register all food/drink consumption in MyFitnessPal or similar applications"
